---
title: "Lab 6 with plotly"
author: "Kat Vrotsos"
format: dashboard
embed-resources: true
orientation: rows
---

```{r}
#| label: load-packages
library(tidyverse)
library(palmerpenguins)
library(colorblindr)
library(gapminder)
library(plotly)
```

# Lab 4: Palmer Penguins

## Graphs from Lab 4 {.sidebar}

The following graphs were created using the **penguins dataset** from the R package **{palmerpenguins}**.

## Row {.panel height="10%"}

The following graphs display Bill Length vs. Bill Depth in Millimeters by Penguin Species using different colorblind friendly scales.

## Row {.tabset}

#### Okabe Ito

```{r}
penguins |>
  ggplot(aes(bill_length_mm, bill_depth_mm)) +
  geom_point(aes(color = species)) +
  scale_color_OkabeIto() +
  labs(
    title = 'Bill Length vs. Bill Depth in Millimeters by Penguin Species',
    subtitle = 'Okabe-Ito Colors',
    x = 'Bill Length (mm)',
    y = 'Bill Depth (mm)',
    color = 'Species'
  ) +
    theme_minimal()
```

#### Viridis Plasma

```{r}
penguins |>
  ggplot(aes(bill_length_mm, bill_depth_mm)) +
  geom_point(aes(color = species)) +
  scale_color_viridis_d(option = "plasma") +
  labs(
    title = 'Bill Length vs. Bill Depth in Millimeters by Penguin Species',
    subtitle = 'Viridis Discrete Colors',
    x = 'Bill Length (mm)',
    y = 'Bill Depth (mm)',
    color = 'Species'
  ) +
    theme_minimal()
```

#### ColorBrewer Set2

```{r}
penguins |>
  ggplot(aes(bill_length_mm, bill_depth_mm)) +
  geom_point(aes(color = species)) +
  scale_color_brewer(palette = "Set2") +
  labs(
    title = 'Bill Length vs. Bill Depth in Millimeters by Penguin Species',
    subtitle = 'ColorBrewer Set2 Colors',
    x = 'Bill Length (mm)',
    y = 'Bill Depth (mm)',
    color = 'Species'
  ) +
  theme_minimal()
```

# Lab 5: Gapminder

## Graphs from Lab 4 {.sidebar}

The following graphs were created using the **Gapminder dataset** from the R package **{gapminder}**.

## Row {.panel height="10%"}

The following graphs display 2007 GDP per Capita by Country in the Americas as a dot plot and lollipop chart.

## Row {.tabset height="90%"}

#### Dot Plot
```{r}
gapminder |> 
  filter(year == 2007, continent == 'Americas') |>
  mutate(country = fct_reorder(country, gdpPercap, .desc = TRUE)) |>
  ggplot(aes(gdpPercap, country)) +
  geom_point(size = 4, color = "#0072B2") +
  scale_x_continuous(labels = scales::dollar) +
  labs(x = "GDP per Capita",
       y = 'Country',
       title = "2007 GDP per Capita by Country in the Americas") +
  theme_minimal()
```

#### Lollipop Chart
```{r}
gapminder |> 
  filter(year == 2007, continent == 'Americas') |>
  mutate(country = fct_reorder(country, gdpPercap, .desc = TRUE)) |>
  ggplot(aes(gdpPercap, country)) +
  geom_point(size = 4, color = "#0072B2") +
  geom_segment(aes(x = 0, xend = gdpPercap, y = country, yend = country), color = "grey") +
  scale_x_continuous(labels = scales::dollar) +
  labs(x = "GDP per Capita",
       y = 'Country',
       title = "2007 GDP per Capita by Country in the Americas") +
  theme_minimal()
```

# Using the {plotly} package in R

## Row
```{r}
p <- penguins |>
  ggplot(aes(bill_length_mm, bill_depth_mm)) +
  geom_point(aes(color = species)) +
  scale_color_brewer(palette = "Set2") +
  labs(
    title = 'Bill Length vs. Bill Depth in Millimeters by Penguin Species',
    subtitle = 'ColorBrewer Set2 Colors',
    x = 'Bill Length (mm)',
    y = 'Bill Depth (mm)',
    color = 'Species'
  ) +
  theme_minimal()

ggplotly(p)
```

